A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-15 EvoPar2017/paper.Rnw
bib added

Recent works have been using crowdsourcing in order to train robots 
for human interaction, a representative work of this trend is that of  
Anetsberger & Bongard in which they propose training simulated robots 
the grounding of language symbols. They do this by using human 
observers that issue arbitrary commands to these robots via the web, 
providing positive or negative reinforcement in response to the
robot’s resulting actions. For interaction, they use the Twitch 
video streaming platform where users can issue commands through the
platform's integrated chat service. Subjects were incentivized to 
interact with the system by GUI features that provided participants
with a sense of involvement with the simulation. This kind of systems
could add additional dynamics, because users can collaborate or 
even compete with each other when issuing their commands.

>>>>

Recent works have been using crowdsourcing in order to train robots 
for human interaction, a representative work of this trend is that of  
Anetsberger & Bongard \cite{anetsbergerrobots} in which they propose 
training simulated robots  the grounding of language symbols. They do this by using human 
observers that issue arbitrary commands to these robots via the web, 
providing positive or negative reinforcement in response to the
robot’s resulting actions. For interaction, they use the Twitch 
video streaming platform where users can issue commands through the
platform's integrated chat service. Subjects were incentivized to 
interact with the system by GUI features that provided participants
with a sense of involvement with the simulation. This kind of systems
could add additional dynamics, because users can collaborate or 
even compete with each other when issuing their commands.
